### 2016-08-28 ReviewComments/review1.tex
Review Response
responses

\response{We agree that utilizing advanced Spark features would 
improve our solutions. We do not include these optimization in-depth
because in this work we set out focus on solving the challenges
in parallelizing the GCMP mining algorithms.
Nevertheless, we would improve and open-source a Spark-tailored
version of SPARE in the future.
}

>>>>

\response{We agree that utilizing advanced Spark features would 
improve our solutions. In this work, we do not include 
these optimization in-depth because we set out focus 
on solving the challenges in parallelizing the 
GCMP mining algorithms.
We are also in progress of open-sourcing a Spark-tailored
version of SPARE.
}

### 2016-08-28 ReviewComments/review2.tex
Review Response
responses

\response{
We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
modeling lies in unifying existing movement patterns in the trajectory domain. 
The gap parameter is naturally introduced to 
solve the loose-connection anomaly (as in Figure 2).
%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
In the revision, we add Section 2.5 to accredit the origin of \emph{gap} concept
and distinguish the sequential mining problem with our problem. 
}

@@

\response{We agree that domain-specific constraints
on spatiotemporal mining could be similar to GCMP.
However, these domain-specific constraints 
are nontrivial to be generalized. Since our GCMP model as well as solutions
do not leverage domain knowledge, we can support
pattern discovery in a broader context. We add the discussion in Section 2.3.
}

>>>>

\response{
We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
modeling lies in unifying existing movement patterns in the trajectory domain. 
The gap parameter is naturally introduced to 
solve the loose-connection anomaly (as in Figure 2).
%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
and distinguish the sequential mining problem with our problem. 
}

@@

\response{We agree that domain-specific constraints
on spatiotemporal mining could be similar to GCMP.
However, these domain-specific constraints 
are nontrivial to be generalized. Since our GCMP model and technical solutions
do not leverage domain knowledge, we can support
pattern discovery in a broader context. We add a discussion in Section 2.3.
}

### 2016-08-28 ReviewComments/review3.tex
Review Response
responses

\response{
We agree that leveraging more advanced Spark features
could further improve the performance of our solutions. 
We do not heavily leverage these features because 
we wish to focus on solving how to design parallel GCMP mining algorithms.
%to provide a general parallel framework which does not tie to Spark.
Nevertheless, we are in progress to develop and open-source 
a better SPARE version with Spark-tailored optimization.

In the revision, we try to add a DataFrame based TRPM solution 
which aims to leverage the window functions in Spark-SQL.
However, to the best of our efforts, we could not achieve this goal in a short time. 
The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
is nontrivial. Nevertheless, we expect less performance
boost from TRPM even with UDAF support. This is because the Line sweep algorithm is not
properly reducible, where Spark system would fail to leverage the partial aggregates
across multiple windows. Then, it would be equivalent to our current TRPM
implementation.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable. 
}

@@

\response{ We use all 16 cores in a single node in our settings. We revise the description in Section 6.2.3.
}

>>>>

\response{
We agree that leveraging more advanced Spark features
could further improve the performance of our solutions. 
We do not heavily leverage these features because 
we wish to focus on designing parallel GCMP mining algorithms.
%to provide a general parallel framework which does not tie to Spark.
Nevertheless, we are in progress in developing
a better open-sourced version with Spark-tailored optimization.

In the revision, we try to add a DataFrame based TRPM solution 
which aims to leverage the window functions from Spark-SQL.
However, to the best of our efforts, we could not achieve this goal in a short time. 
The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
is nontrivial. Nonetheless, we expect less performance
boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
properly reducible, where Spark system would fail to leverage the partial aggregates
across multiple windows. As a result, it would be equivalent to our current TRPM
solution where windows are processed independently in parallel.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable. 
}

@@

\response{ We use all cores in a single node to conduct the experiments. We revise the description in Section 6.2.3.
}

### 2016-08-28 sec6_experiment.tex
Review Response
responses

\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core \revised{(i.e., single node with 3 executors)} environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.

>>>>

\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core \revised{(i.e., a single node with four executors)} environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.
